---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Sean2025)
```

# introduction

This vignette demonstrates the functionality of the MATH4753Sean2025 package, which functions such as myboot2, mymlnorm, myncurve, myclt, ntickets, myf, mysq and the dataset FIREDAM

# FIREDAM Dataset

```{r}
head(fire)
```

# myboot2

Compute a 95% bootstrap CI for the median fire damage

```{r}
set.seed(123)
boot_result <- myboot2(iter = 1000, x = fire$DAMAGE, fun = median, alpha = 0.05)
boot_result$ci
```

# mymlnorm

Fit a normal distribution
```{r}
ml_result <- mymlnorm(
  x = fire$DAMAGE,
  mu = seq(10, 25, length = 100),
  sig = seq(3, 8, length = 100)
)
```

# myncurve 

Plot a normal curve with mean/sd and shade P(X ≤ 20)
```{r}
myncurve(
  mu = mean(fire$DAMAGE),
  sigma = sd(fire$DAMAGE),
  a = 20
)
```

# myclt

Simulate sums of uniform variables (n = 50):
```{r}
myclt(n = 50, iter = 1000, a = 0, b = 10)
```

# ntickets

Find optimal tickets sold
```{r ntickets-example, fig.width=10, fig.height=6}
ntickets(N = 400, gamma = 0.02, p = 0.95)
```

# myf

Model fire damage with a knot at 3 miles

```{r}
coef_example <- c(10, -2, 5)
myf(x = fire$DISTANCE, xk = 3, coef = coef_example)
```

# mysq

Takes the square of values

```{r}
mysq(1:10)
```
